\documentclass{amsart}

\usepackage{setspace}
\begin{document}

\spacing{1.3}

\section*{Ovals Problem is not affine-invariant}

Take an affine transformation \(\gamma \mapsto A \gamma + b\). The \(b\) doesn't enter into the problem. Let's write \(\bar{\gamma} = A \gamma\). Define
\[
c = \|A\gamma'|/\|\gamma'\|
\]

Note that \(c\) is non-constant along the curve in general! In the particular case \(A \in O(2)\), \(c \equiv 1\).

Then 
\begin{align}
d\bar{s} &= c ds \\
\partial_{\bar{s}} &= (1/c) \partial_s \\ 
\bar{\kappa} &= (1/c^3) \kappa
\end{align}.

Incidentally, these relations lead to the affine-invariance of \(\int \kappa^{1/3} ds\).

Now look at the Rayleigh quotient:
\[
\int (f_{\bar{s}})^2 + \bar{\kappa}^2 f^2 d\bar{s} = \int \left(\frac{1}{c^2} (f_s)^2 + \frac{1}{c^6} \kappa^2 f^2\right) c ds = \int \frac{1}{c} (f_s)^2 + \frac{1}{c^5} \kappa^2 f^2 ds
\]

The scaling of \(c\) is all wrong here and it doesn't seem possible to make this work unless \(c \equiv 1\). 

Therefore the family of ovals does not correspond to a 1-parameter subgroup of affine transformations! The problem is if these transformations are required to preserve length, then it seems they must be orthogonal transformations, but then you can't get a family of ellipses this way!

Maybe, it's possible to transform \(f\) as well to make this work, say by initially normalising \(f\) to have \(\int f^2 = 1\) and then allow our affine transformations to vary length, but adjust for this in scaling \(f\) accordingly? Still doesn't seem likely to work...

\section*{Latest approach... Wirtinger inequality}

Reference:  Chavel's book on isoperimetric inequality.   

\bigskip
\textbf{Theorem:} Let $f:[0,L]\rightarrow \mathbb{R}$ satisfy $\int_0^L f\,dx=0$.   Then 
\[\int_0^L |f'|^2 \,dx\ge \frac{4\pi^2}{L^2}\int_0^L f^2\,dx.\tag{WI}\]
Equality happens in the case that $f=a_{-1}exp(-2\pi i x/L)+ a_{1}exp(2\pi i x/L).$

\bigskip

Now let $X:[0,L]\rightarrow \mathbb{R}^2$ be an embedding of a closed curve.  (Not necessarily parameterized w.r.t. arc-length, and in fact in our use of this, it explicitly it is NOT-- $u$ is the arc-length parameter of the original curve, which is NOT $X$.)

\textbf{Let us assume that $\int X \,du =0$. }  

Then apply the WI to each of the coordinate functions $(X_1,X_2)$ of $X$.   

We find
\[ \int |(X_i)_u|^2 \,du \ge \frac{4\pi^2}{L^2}\int |X_i|^2\,du  \quad\quad \text{ for }i=1,2.\]

Sum over $i=1,2$: 
\[ \label{BT} \int |X_u|^2 \,du \ge \frac{4\pi^2}{L^2}\int |X|^2\,du .  \tag{BT}\]

Claim: equality in the case that $X=\cos u \mathbf{v_1}+ \sin u \mathbf{v_2}$ (i.e. in family of ovals) (have not checked this).

If it happens to be the case that $L=2\pi$, this is exactly what we're after:  since we can set $X=f(u)T(u)$ (where $f$ is the eigenfunction and $T$ is the tangent in the original formulation of the problem, and $u$ is arclength of the original $\gamma$).  (I call this the BT setting, as it was what Burchart-Thomas were using.)  Then $X_u= f' T+ fT_u= f'T+ fkN$, and so \eqref{BT} becomes
\[ \int f'^2 + k^2 f^2 \,du \ge \int f^2\,du, \]
as required.

(Tangentially:   this approach gives a nice proof of the fact that $\int_\gamma k^2 \ge \frac{4\pi^2}L$.)

So what is the problem here?  The assumption that $\int X \,du=0$.   

If $X$ is given by $fT$, and $T$ is the tangent of the closed curve in the original formulation, then what is actually satisfied is 
\[ \int \frac{X(u)}{|X(u)|}\,du = \int T \,du= 0.\]

It is not generally true that $\int X=0$.   (Except in the circle case, when $f$ is constant).   (It is also true in the oval case, when $X_0=\cos u \mathbf{v_1}+ \sin u \mathbf{v_2}$).   

Some ideas:   
\begin{enumerate}
\item Translate $X$ so we satisfy $\int X=0$.  Lefthand side is nice, messes around with the RHS. \label{translate}

\item Or we could just reparameterise so that $ds=du/|X(u)|$.   Then we find that $\int X \,ds=0$, but we then have to integrate against $ds$ throughout... introducing a bunch of nasty $|X(u)|$ terms in our expression.     Which correspond to $f$.

\item There is something about the equality case in WI that connects to the ellipses of the ovals problem.

\item apply WI directly to $X/|X|$?

\item The expression \eqref{BT} IS affine invariant, right?



\end{enumerate}

\textbf{Further look at the translating idea, (\ref{translate}).}

Same set up, but this time we assume $\int \frac{X}{|X|}\,du=0$. 

Let $\tilde{X}=X-Y$, where $Y$ is chosen so that $\int\tilde{X}\, du=0$.    This implies that $Y=\frac1L\int X \,du$.    Then we can apply \eqref{BT} to $\tilde{X}$, so that 
\[  \int |\tilde{X}_u|^2 \,du \ge \frac{4\pi^2}{L^2}\int |\tilde{X}|^2\,du , \]
so
\begin{equation} \int |{X}_u|^2 \,du \ge \frac{4\pi^2}{L^2}\int |{X}-Y|^2\,du , \label{tildy}\end{equation}

\emph{Do something with the equality case:  the equality case implies that $Y=0$.}

If I had $\int|X-Y|^2\ge\int|X|^2$ then I would be done, but that looks flat-out wrong, since 
\[\int |X-Y|^2 \, du = \int |X|^2- \frac1L\left(\int X\right)^2\]
which is \emph{strictly} less than $\int |X|^2$-- except of course in the case that $\int X=0$ (in which case we'd be done already).   

I still haven't used $\int \frac{X}{|X|}\,du=0$, but it's certainly the case that $X$ can satisfy that, but not $\int X=0$.  

\eqref{tildy} gives 
\begin{equation}\frac{ \int |{X}_u|^2 \,du}{ \frac{4\pi^2}{L^2}\int |{X}-Y|^2\,du }\ge 1, \label{stupid translate} \end{equation}

I can't see any way forward here.   Unless it is to use this expression to show the impossibility of a counter example?

Sketch:   \begin{itemize}
\item we get equality in \eqref{stupid translate} when $X=\sin $ etc, this implies $Y=0$. 
\item For all other $X$, we have
\begin{equation}\frac{ \int |{X}_u|^2 \,du}{ \frac{4\pi^2}{L^2}\int |{X}-Y|^2\,du }> 1,  \end{equation}
\item but we know that in the case that $\int X\not=0$, $\int |{X}-Y|^2\,du < \int |X|^2$, so 
\begin{equation}
\frac{ \int |{X}_u|^2 \,du}{ \frac{4\pi^2}{L^2}\int |{X}-Y|^2\,du }> \frac{ \int |{X}_u|^2 \,du}{ \frac{4\pi^2}{L^2}\int |{X}|^2\,du },  \end{equation}
\item to show a counterexample, choose $Y$ so that $\int |X-Y|^2$ is large enough that 
\[1\ge \frac{ \int |{X}_u|^2 \,du}{ \frac{4\pi^2}{L^2}\int |{X}-Y|^2\,du }\]
\item this would then give a counterexample to 
\begin{equation}\frac{ \int |{X}_u|^2 \,du}{ \frac{4\pi^2}{L^2}\int |{X}|^2\,du }\ge 1, \label{stupid translate} \end{equation}
\item but we can't choose such a $Y$, because of (6).
\end{itemize}
\bigskip

\textbf{Look at the reparameterization idea, (2):}

Here we start by assuming  $\int \frac{X}{|X|}\,du=0$.  Then make a change of variables, $s(u)=\int \,ds=\int \frac{du}{|X|}$.   That is, $du/ds=|X|$.  

This then satisfies $\int X(s)\,ds=\int  \frac{X}{|X|}\,du=0$, so \eqref{BT} gives
\[ \int_0^{s(L)} |X_s|^2 \,ds \ge \frac{4\pi^2}{\tilde{L}^2}\int |X|^2\,ds\]
where $\tilde{L}=\int_0^L \,ds$.  Converting back to $u$ gives
\[ \int_0^{L} |X_u|^2|\frac{du}{ds}|^2 \,\frac{du}{|X|} \ge \frac{4\pi^2}{\tilde{L}^2}\int |X|^2\,\frac{du}{|X|}\]
thus
\[ \int_0^{L} |X_u|^2|X| \,du\ge {4\pi^2}\left(\int_0^L |X|^{-1}\,du \right)^{-2}\int |X|\,{du}.\]

This is ridiculous.

\clearpage

\section*{Next idea:  Affine $+$ Wirtinger}

\textbf{The plan}
 
 1.  Wirtinger inequality for closed curves:  if $\int Z du =0$ then 
 $$\int |Z_u|^2 \,du \ge \frac{4\pi^2}{L^2}\int |Z|^2 \,du  \quad \quad \text{(WI)}$$
 
 2.  Let $X$ be fixed closed curve with $$\int \frac{X}{|X|}\,du =0.$$
 
 3.  Let $A$ be affine (in fact linear).  \textbf{Claim: }Then $X\rightarrow AX$ keeps 
 \begin{equation}\frac{\int |X_u|^2 du }{\int |X|^2 \,du}  \label{this equation} \end{equation}
 the same but not $$\int X\,du.$$
 
 4.   \textbf{Claim:} We can choose $A$ so that $Y=AX$ satisfies $\int Y \,du =\int AX\,du=0.$
 
 5.  Then $$\int |Y_u|^2 \,du \ge \frac{4\pi^2}{L^2}\int {|Y|^2}\,du,$$ by (WI).
 
 6.  And so $$\int |X_u|^2 \,du \ge \frac{4\pi^2}{L^2}\int {|X|^2}\,du,$$


Cautions:  what is the deal with length under $A$? That is, the quantity in \eqref{this equation} may be invariant under $A$, but what about
\begin{equation}\frac{ \int |{X}_u|^2 \,du}{ \frac{4\pi^2}{L^2}\int |{X}|^2\,du } ? \end{equation}

Am I using the condition $\int X/|X|$?



\end{document}